%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MCM/ICM LaTeX Template %%
%% 2025 MCM/ICM %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Format
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{left=1in, right=0.75in, top=1in, bottom=1in}

\newcommand{\Problem}{F}
\newcommand{\Team}{2500434}

\usepackage{newtxtext}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{newtxmath}
\usepackage[pdftex]{graphicx}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}
\usepackage{changepage}

% Page Settings
\pagestyle{fancy}
\lhead{Team \# \Team}
\rhead{Page \thepage\ of \pageref{LastPage}}

% Mathematical env.
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}{Definition}

% Format of table of contents
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\contentsname}{\begin{center} INDEX \end{center}}

% Format of subsection and subsubsection
\titleformat{\section}{\bfseries\raggedright\Large}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\raggedright}{\thesubsection}{1em}{}{}
\titleformat{\subsubsection}{\bfseries}{\hspace*{2em}\thesubsubsection}{1em}{}{}

% CoverPage Design
\begin{document}
\graphicspath{{.}}  % Place the graphic file in the same directory as the main document
\DeclareGraphicsExtensions{.pdf, .jpg, .tif, .png}
\thispagestyle{empty}
\vspace*{-16ex}
\centerline{
\begin{tabular}{*3{c}}
	\parbox[t]{0.3\linewidth}{\begin{center}\textbf{Problem Chosen}\\ \Large \textcolor{red}{\Problem}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{2025\\ MCM/ICM\\ Summary Sheet}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{Team Control Number}\\ \Large \textcolor{red}{\Team}\end{center}}	\\
	\hline
\end{tabular}}

% Summary %
\begin{center}
	\fontsize{16}{19}\selectfont \textbf{Modeling Cybercrime Governance: When Policies Meet the Attackers} \\
	\bigskip
	\fontsize{16}{19}\selectfont \textbf{Summary} \\
\end{center}
\begin{adjustwidth}{2em}{2em}
	\hspace*{1.5em} In recent years, especially since 2012, the number of cyber crimes in various countries has risen sharply.
	Developed countries, led by the United States and Europe, are more seriously affected by cyberattacks,
	and this trend may cause national data leakage and cause huge economic losses.
	Therefore, models are needed to quantify the impact of the cybercrime situation in each country under various factors.

	By the size of the $GCI$ indicator, we divided the countries into five gradients.
	The typical countries in each division are selected according to the variance and the amount of data.
	The typical countries based on this division have universality in data,
	which means that the conclusions obtained from the separate detailed analysis of the typical countries can also be applied to other countries in the same echelon.

	By filtering and refining the $json$ data information in the $VCDB$ repository,
	we establish a data-driven model to solve the annual cyber crime situation around the world, and display it in the form of heat maps.
	As for the processing of refined indicators (successful, thwarted, reported, prosecuted),
	we also first filter the data, and modify the screening range to Success, Reported, Near Miss and False positive.
	Then the corresponding data-driven model is established and displayed with the heat map.

	For the global cybercrime situation under the influence of law and policy,
	we first obtain the total population of each country in the world, filter and process the data, and then obtain the annual average crime rate of each country.
	We then collected all the cybersecurity laws and regulations from 2000 to 2023 for a typical country in different categories,
	in order to build a large data-driven model to correlate legal policies and crime rates for a typical country.
	At the same time, the corresponding line chart can be drawn to find out which bills in which years of typical countries have immediate effects,
	that is, they play an obvious role in the control of cyber crime in that year.
	Next, we analyze the law rate policy and typical national network security management through $Poisson$ regression.
	Because the timeliness of legal policies should be considered.

	To analyze the correlation between the distribution of cybercrime and national demographic data
	(such as Internet use, per capita wealth level, education level, etc.) indicators,
	we first collected and processed the relevant data on various refined indicators of typical countries in the past 20 years,
	and then used $TOPSIS$ based on entropy weight method to judge the correlation.
	Then calculate the $Spearman$ coefficient to quantitatively assess the correlation between the refinement indicators and cybercrime,
	so as to determine which specific demographic data refinement indicators have the greatest impact on dealing with cybercrime.

	Considering the above aspects, we can control the network crime rate to a great extent,
	so as to make the national network public security system more perfect and stable.
\end{adjustwidth}

\newpage
\tableofcontents
\newpage

\section{Introduction}\label{sec:introduction}
\input{introduction} %1

\section{Symbol and Assumptions}\label{sec:symbol-and-assumptions}
\input{symbol-and-assumptions} %2

\section{A Data-Driven Model for Global Cybercrime Hotspot Mapping}
\label{sec:a-data-driven-model-for-global-cybercrime-hotspot-mapping}
\input{a-data-driven-model-for-global-cybercrime-hotspot-mapping} %3

\section{Policy Identification and Analysis}\label{sec:policy-identification-and-analysis}
\input{policy-identification-and-analysis} %4

\section{Correlation Between National Demographics and Cybercrime Distribution}
\label{sec:correlation-between-national-demographics-and-cybercrime-distribution}
\input{correlation-between-national-demographics-and-cybercrime-distribution} %5

\section{Future Work}\label{sec:future-work} %6
\input{future-work}

\section{Strengths \& Weaknesses}\label{sec:strength-&-weakness}
\input{strength-&-weakness} %7

\newpage
\section*{\begin{center} Memo \end{center}}\label{sec:memo}
\input{memo} %8
\newpage

\bibliographystyle{unsrt}
\bibliography{references} %9

\newpage
\section*{\centerline{\underline{Report on Use of AI}}}
\input{report-on-use-of-ai}

\end{document}
